A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-07-30 latex/paper.tex
Changed url for interactive figures

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/spark-inc-baseline.html?download=1}{
            \includegraphics[clip,width=\columnwidth,
            height=0.15\textheight]{images/spark_inc_gantt.png}}
        \caption{Spark}\label{fig:inc_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/dask-bag-inc-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_inc_gantt.png}}
        \caption{Dask Bag}\label{fig:inc_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/dask-delayed-inc-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_inc_gantt.png}}
        \caption{Dask Delayed}\label{fig:inc_dask_delayed_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/dask-futures-inc-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/futures_inc_gantt.png}}
        \caption{Dask Futures}\label{fig:inc_dask_futures_gantt}
    \end{subfigure}
    \caption{Incrementation: 125 blocks, 10 iterations, \SI{4}{\second} delay, 8 workers,
8 CPUs/worker}\label{fig:inc_gantt}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/spark-histo-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_histo_gantt.png}}
        \caption{Spark}\label{fig:histo_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/dask-bag-histo-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_histo_gantt.png}}
        \caption{Dask Bag}\label{fig:histo_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/dask-delayed-histo-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_histo_gantt.png}}
        \caption{Dask Delayed}\label{fig:histo_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram (Python): 125 blocks, 8 workers, 8
    CPUs/worker}\label{fig:histo_gantt}
\end{figure}

@@

\begin{figure}[!tb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/spark-histo_np-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_histo_np_gantt.png}}
        \caption{Spark}\label{fig:histo_np_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/dask-bag-histo_np-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_histo_np_gantt.png}}
        \caption{Dask Bag}\label{fig:histo_np_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/dask-delayed-histo_np-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_histo_np_gantt.png}}
        \caption{Dask Delayed}\label{fig:histo_np_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram (NumPy): 125 blocks, 8 workers, 8
    CPUs/worker}\label{fig:histo_np_gantt}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/spark-bids-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_bids_gantt.png}}
        \caption{Spark}\label{fig:bids_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/dask-bag-bids-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_bids_gantt.png}}
        \caption{Dask Bag}\label{fig:bids_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/dask-delayed-bids-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_bids_gantt.png}}
        \caption{Dask Delayed}\label{fig:bids_dask_delayed_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/dask-futures-bids-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/futures_bids_gantt.png}}
        \caption{Dask Futures}\label{fig:bids_dask_futures_gantt}
    \end{subfigure}
    \caption{BIDS App example: 8 workers}\label{fig:bids_gantt}
\end{figure}

>>>>

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-inc-baseline.html}{
            \includegraphics[clip,width=\columnwidth,
            height=0.15\textheight]{images/spark_inc_gantt.png}}
        \caption{Spark}\label{fig:inc_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-inc-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_inc_gantt.png}}
        \caption{Dask Bag}\label{fig:inc_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-inc-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_inc_gantt.png}}
        \caption{Dask Delayed}\label{fig:inc_dask_delayed_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-futures-inc-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/futures_inc_gantt.png}}
        \caption{Dask Futures}\label{fig:inc_dask_futures_gantt}
    \end{subfigure}
    \caption{Incrementation: 125 blocks, 10 iterations, \SI{4}{\second} delay, 8 workers,
8 CPUs/worker}\label{fig:inc_gantt}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_histo_gantt.png}}
        \caption{Spark}\label{fig:histo_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_histo_gantt.png}}
        \caption{Dask Bag}\label{fig:histo_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_histo_gantt.png}}
        \caption{Dask Delayed}\label{fig:histo_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram (Python): 125 blocks, 8 workers, 8
    CPUs/worker}\label{fig:histo_gantt}
\end{figure}

@@

\begin{figure}[!tb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-histo_np-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_histo_np_gantt.png}}
        \caption{Spark}\label{fig:histo_np_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-histo_np-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_histo_np_gantt.png}}
        \caption{Dask Bag}\label{fig:histo_np_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-histo_np-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_histo_np_gantt.png}}
        \caption{Dask Delayed}\label{fig:histo_np_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram (NumPy): 125 blocks, 8 workers, 8
    CPUs/worker}\label{fig:histo_np_gantt}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-bids-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_bids_gantt.png}}
        \caption{Spark}\label{fig:bids_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-bids-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_bids_gantt.png}}
        \caption{Dask Bag}\label{fig:bids_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-bids-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_bids_gantt.png}}
        \caption{Dask Delayed}\label{fig:bids_dask_delayed_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-futures-bids-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/futures_bids_gantt.png}}
        \caption{Dask Futures}\label{fig:bids_dask_futures_gantt}
    \end{subfigure}
    \caption{BIDS App example: 8 workers}\label{fig:bids_gantt}
\end{figure}
